E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-11 System/proof_of_concept.tex
chap4 added

\section{Proof of Concept Attacks}
The previous section (Section~\ref{Arch:Test}) discussed in detail how we verified that our system functions according to our expectations. This section describes how we validated our expectations. In order to do this, we constructed three sets of web applications in PHP, Python, and Ruby. Each of these applications was a simple web app that accepted user input to construct and send an E-Mail.

>>>>

\subsection{Proof of Concept Attacks}
The previous section (Section~\ref{Arch:Test}) discussed in detail how we verified that our system functions according to our expectations. This section describes how we validated our expectations. In order to do this, we constructed three sets of web applications in PHP, Python, and Ruby. Each of these applications was a simple web app that accepted user input to construct and send an E-Mail.

### 2016-05-11 exp_setup.tex
chap4 added

\chapter{Evaluation}
This chapter describes the experimental setup for our project including the servers used, the software and the platforms involved, the languages used, and the task queue system that was used for parallelism. We follow this up with our evaluation of the system, with a test suite, and proof of concept examples.

>>>>

\section{Evaluation}
This chapter describes the experimental setup for our project including the servers used, the software and the platforms involved, the languages used, and the task queue system that was used for parallelism. We follow this up with our evaluation of the system, with a test suite, and proof of concept examples.
